{\fontfamily{ptm}\selectfont Lorum ipsum}

### 2025-07-02 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

\newcommand{\cov}{\ensuremath{\operatorname{Cov}}}

@@

\author{
    Author 1 Name, Author 2 Name
    \thanks{
        Subject type, Some Department of Some University, Location of the University,
        Country. E-mail: \texttt{author.name@university.edu}.
    }
}

@@

        \begin{lemma}[range of the momentum sequence in SNAPG-V2]

@@

@@

@@

            Starting with (a) we have: 

@@

>>>>

\newcommand{\cov}{\ensuremath{\operatorname{Cov}}}
\newcommand{\var}{\ensuremath{\operatorname{Var}}}

@@

\author{
    HONGDA LI
    \thanks{
        University of British Columbia Okanagan,
        Canada. E-mail: \texttt{alto@mail.ubc.ca}.
    }
}

@@

        \begin{lemma}[range of the momentum sequence in SNAPG-V2]\label{lemma:snapg-v2-seq-range}

@@

            Let $F$ satisfies assumption \ref{ass:interp-hypothesis}. 
            Suppose that an algorithm satisfying Definition \ref{def:snapg-v2} takes this $F$, for all $k \ge 1$, it has the following inequality 
                & \mathbb E_k\left[F_{I_k}(x_{k})\right] 
                - F(\bar x) 
                + \mathbb E_k\left[
                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                \right]
                        \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
                        - F(\bar x)
                        + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
                    + \mathbb E_k\left[
                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 

@@

                \item[(h)] Because we assumed interpolation hypothesis in Assumption \ref{ass:interp-hypothesis}, it has $\mathbb E[F_{I_k}(\bar x)] = F(\bar x)$ for all $\bar x$ that is a minimizer of $F$. 

@@

            For all $k \ge 1$, starting with (a) we have: 

@@

                \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) 
                    + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
                \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) 
                    - \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                    + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
                &= (\alpha_k - 1)F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) + F_i(\bar x)
                    - \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                    + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
                &= (1 - \alpha_k)\left(
                    F_i(x_{k - 1}) - F_i(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
                    \\ & \quad
                    - \left(
                        F_i(x_{k}) - F_i(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2}\Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
            Recall that $i = I_k$ is the random variable from Definition \ref{def:snapg-v2}. 
            Rearranging the last expression in the above equality chain can be conveniently written as
            \begin{align}
                    & \left(
                        F_{I_k}(x_{k}) - F_{I_k}(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                    \\ &\le 
                        F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
                        + \frac{\alpha_k(\mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
                        + \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
            \label{ineq:snapg2-one-step-presult1}\end{align}
            Recall $\mathbb E_k$ denotes the conditional expectation on $I_0, I_1, \ldots, I_{k - 1}$. 
            Taking the conditional expectation on the LHS of the \eqref{ineq:snapg2-one-step-presult1} yields: 
                & \mathbb E_k\left[
                    F_{I_k}(x_{k}) - F_{I_k}(\bar x) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                \right]
                &\underset{\text{(h)}}{=}
                \mathbb E_k\left[F_{I_k}(x_{k})\right] 
                - F(\bar x) 
                + \mathbb E_k\left[
                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                \right]. 
            On the RHS of \eqref{ineq:snapg2-one-step-presult1}, using the linearity property while taking the conditional expectation yields: 
                & \mathbb E_k\left[
                        F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert v_{k - 1} - \bar x\Vert^2
                \right]
                    + \mathbb E_k \left[
                        \frac{\alpha_k(\mu - \mu^{(I_k)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
                    \right]
                    + \mathbb E_k\left[
                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}\Vert x_{k - 1} - v_{k - 1} \Vert^2
                    \right]
                &\underset{\text{(1)}}{=} 
                        \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
                        -\mathbb E_k [F_{I_k}(\bar x)] 
                        + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
                    + \mathbb E_k \left[
                        \frac{\alpha_k(\mu - \mu^{(I_k)})}{2} 
                    \right]\Vert \bar x - v_{k - 1}\Vert^2
                    + \mathbb E_k\left[
                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
                &\underset{\text{(h)}}{=} 
                        \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
                        - F(\bar x)
                        + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
                    + \mathbb E_k \left[
                        \frac{\alpha_k(\mu - \mu^{(I_k)})}{2} 
                    \right]\Vert \bar x - v_{k - 1}\Vert^2
                    + \mathbb E_k\left[
                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
                &\underset{\text{(2)}}{=}
                        \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
                        - F(\bar x)
                        + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
                    + \mathbb E_k\left[
                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2
            We note that at label (1), we used the fact that $\alpha_k$ is a constant and, $x_{k - 1}, v_{k - 1}$ only depends on random variable $I_0, I_1, \ldots, I_{k - 1}$ hence it falls out of the conditional expectation $\mathbb E_k$. 
            At label (2), we used assumption (Assumption \ref{ass:sum-of-many}) that the averages of all the $\mu^{(I_k)}$ on each $F_{I_k}$ equals to $\mu$ hence, the expectation evaluates to zero by linearity of the expected value operator. 
            Combing the above results on the expectation of RHS, and LHS of \eqref{ineq:snapg2-one-step-presult1}, we have the one step inequaity in expectation: 
                & \mathbb E_k\left[F_{I_k}(x_{k})\right] 
                - F(\bar x) 
                + \mathbb E_k\left[
                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                \right]
                        \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] 
                        - F(\bar x)
                        + \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\right]\Vert v_{k - 1} - \bar x\Vert^2
                    + \mathbb E_k\left[
                        \frac{(\alpha_k - 1)\mu^{(I_k)}\left(L_k\alpha_k - \mu^{(I_k)}\right)}{2\left(L_k - \mu^{(I_k)}\right)}
                    \right]\Vert x_{k - 1} - v_{k - 1} \Vert^2. 
